### 2023-01-05 reviews/response.tex

You conclude overall that the QBD-RAP scheme performs better than the uniformisation scheme; however, in my perception through the examples, and also being very much example dependent, my view is a bit muddier. Also, everything seems to be a trade-off between convergence vs. quality. Of course, converging to a useless approximation might not be considered “convergence” at all.
\begin{quote}
    I do not understand this criticism. The QBD-RAP beats uniformisation almost all the time. I do cherry-pick the examples because I am trying to argue that the QBD-RAP method works well for those``typically hard'' examples. What do you mean by convergence and quality? It's converging to the true solution! What is useless about that?
\end{quote}

p.177, mid: you mention the problem of integration errors. Those are, of course, present also in all other cases. How did you control these errors? Did you consider employing Richardson extrapolation to reduce the errors?
\begin{quote}
    I did not specifically control for these errors. I did use the same integration scheme and step size for all methods, so these errors should be somewhat consistent between the methods. I did not use Richardson. 
\end{quote}

\st{Example 7.9: what do you mean by a PDF 1(x < 1). Uniform dist. over (0, 1)?}

What about CPU times for the different experiments? Was the limitation of 21 dimensions dictated by execution times?
\begin{quote}
    I did not measure CPU times.

    I could do higher than dimension 21 for most examples, except Example 7.13 which is limited by simulations.
\end{quote}

While Erlangization/Uniformisation is straightforward and hence automatic to implement, I believe this is not the case for the concentrated ME. Please comment on this.
\begin{quote}
    They are relatively similar to implement. What sort of commentary would this require?
\end{quote}

@@

\pagebreak
\section{Reviewer 2}

\noindent\textbf{2 About the main sections}

Section 2 is of slightly uneven level of detail. Maybe some of the more basic topics are not even necessary. I also suggest re-ordering the subsections from basic to advanced
\begin{quote}
    \begin{itemize}
        \item I'm not sure what the reviewer means by "uneven level of detail" -sure, some sections are more technical than others. But I think that's just the nature of the topics and the they are presented in the detail required to understand the relevant parts of the thesis.

@@

        \item I don't think removing basic topics is the answer. I'd rather explain more and the reader can skip bits they don't think they need.

        \item I like the order of the introduction. It builds in a logical order: some fundamental mathematical concepts -just enought to get going, then I introduce the fluid and fluid-fluid queue, then tools for their approximations, then other sundry mathematical concepts used in the thesis. I don't think suggested order would add value.  
    \end{itemize}
\end{quote}

@@

Section 3 presents the discontinuous Galerkin (DG) method. Unfortunately, no explicit error bounds are available.

Section 4 presents the QBDRAP method. It uses concentrated matrix exponential (CME) functions. It is nice to see that certain properties of CME functions (such as identical real part of all eigenvalues) are utilised.

Sections 5 and 6 proves convergence for QBDRAP. These sections are rather long and heavy, but the arguments are mostly familiar from the literature. Everything is properly referenced. Sections 5 and 6 could be merged into a single section. Section 5 is difficult to follow; maybe arranging the calculations in Sections 5.2 and 5.3 into lemmas or steps would result in a better structure.
\begin{quote}
    \begin{itemize}
        \item Yes, these sections are long and heavy. I think it's hard to avoid. We have talked about this a lot. I am happy with the content of these sections, but I know Peter objects to including some of the details which make the presentation more complex. 
        \item Happy to merge 5 and 6. What do you think? I separated them because they used distinct techniques, but they ultimately combine to prove a single result. 
        \item Happy to add more steps and signposts in Sections 5.2/5.3 or convert them to Lemmas -perhaps structuring as Lemmas is the way to go as it condenses the important points into a single statement and leaves details to a proof, allowing the reader to forget about the details.
    \end{itemize}
\end{quote}

Section 7 presents numerical investigations for a fairly broad selection of examples. Despite the lack of explicit error bounds, we see DG performing well in many cases. Fluid-fluid models are welcome. A general remark: CME distributions only get really concentrated for high orders (dimension). Ideally, I would recommend using at least an order of 30, although I understand there are computational limitations. Either way, it should not be surprising that their performance is not great for orders below 10 or so.
\begin{quote}
    \begin{itemize}
        \item   Not sure what ``fluid-fluid models are welcome'' means.
        \item I went up to order 21 in the numerical investigations. For some of the more trivial examples in this section I could use higher-order approximations. However, for the interesting examples, simulation is required to measure accuracy and this is computationally expensive. I'm already doing \(5\times 10^{10}\) realisations! To me, it seems unlikely that investigation of higher-order examples would reveal much more insight -my intuition is that the error decay of the QBD-RAP method is exponential in the order of the ME used. 
    \end{itemize}
\end{quote}

\noindent\textbf{3 List of minor remarks and typos}

@@

\begin{quote}
    Not sure what's wrong with it...
\end{quote}
\item \st{page 13: 'otherwise it is reflected' I understand why the word 'reflected' is used here, but usually a reflecting boundary condition means evolving with -ci instead of ci. Here, this is simply an absorbing boundary condition, with transition upon reaching the boundary.}

@@

\end{quote}
\item \st{page 17, bottom formula: extra ) bracket}
\item \st{page 18: 'which is only possibly'  'which is only possible'}
\item page 19: 'Conditions on fluid-fluid queues to ensure that (2.20) will be differentiable with respect to y are not known, and here we just assume that it is.' this seems like an innocent assumption. Why don't we have this at least for some nice cases? A few more words on this would be welcome.

@@

\item \st{page 20, third row from top: some ) brackets are missing}
\item \st{page 20: a point masses to a point mass}
\item \st{page 30, before (2.35): extra ) bracket in ()}
\item page 35: Section 2.5.5. about accuracy is indeed very brief and seems highly nonrigorous.

@@

would also help out Cor. 2.6.}
\item \st{page 37, near bottom: possibility defective to possibly defective I recommend a
thorough read-through of Section 2.6.1.}
\item \st{page 39: 'the process may not actually jump at these times' reword to something

@@

    I have moved this section to section 2.3.
\end{quote}
\item \st{page 48, near the top: 'Fubini's Theorem us to' to 'Fubini's Theorem allows us to'}
\item \st{page 53: 'The DG method conserves probability' so any quantity from [0,1] remains

@@

mean something else? Maybe a reference to Cor. 3.1 on page 60? In any case, this
should be clarified here.}
\begin{quote}
    I have clarified that it conserves total probability of the system and added a reference to cor 3.1.

@@

\begin{quote}
    They are only used here, in this specific place, and only takes up less than 2 lines. Do I need to move it?
\end{quote}
\item \st{page 56: There are different choices for the flux rather, for the choice of approximation for the flux, right?}
\item \st{page 60, middle of page: overlong line}

@@

\item \st{page 60, bottom formula, first line: the 'or' part should be re-formulated (e.g.
something like k = l 6 = 0 or K)}
\item \st{page 70, middle: 'we can show even show' to 'we can even show'}
\item \st{page 70: 'on the event that phi(t) is constant, then X(t) moves deterministically' 'then' is unnecessary}
\item \st{page 80, near top: 'Other choices are possible' ... 'are other possible choices' unnecessary repeat}

@@

\item \st{page 88, top line: 'events epochs' to 'event epochs'}
\item \st{page 102, bottom: use the same function (e.g. g(x)) in both formulae}
\item \st{page 104: (5.10) and (5.11) seem to be a single formula broken into two parts
unnecessarily.}

@@

\item \st{page 106, near bottom: 'in terms of the of first return matrices' to 'in terms of the
first return matrices'}
\item \st{page 108, line before (5.25): you could simply write q, r in +, (later as well)}

@@

\item \st{page 151: 'and the last inequality is the Law of total probability' to 'and the last
equality is the Law of total probability'}
\item \st{page 154: 'where the swap of the intergals' to 'where the swap of the integrals'}
\item \st{page 155: 'The probability of 1 is' this looks a bit strange, maybe use A and B to
denote those events}
